RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2023-01-17 jsac.tex
:triangular_flag_on_post: JSAC 230117

	% ? Add an illustration here if space allows
	We also propose a novel cooperative receiver that exploits the double modulation, double fading and symbol period difference to reduce the decoding complexity and improve the primary-backscatter tradeoff.
	As illustrated in Fig.~\ref{fg:energy_distribution}, conditioned on different reflection state hypotheses, the accumulated receive energy per backscatter block follows Gamma distribution with different scale parameters \cite{Qian2017b}.
	\begin{figure}[!t]
		\centering
		\resizebox{0.4\columnwidth}{!}{
			\input{assets/illustration/energy_distribution.tex}
		}
		\caption{
			\gls{pdf} of accumulated receive energy per backscatter block conditioned on different reflection state hypotheses.
			% $z$, $t$, $\mathcal{H}$ and $\mathcal{R}$ denote the accumulated receive energy, decision threshold, reflection state hypothesis, and decision regions, respectively.
		}
		\label{fg:energy_distribution}
	\end{figure}
	Hence, the receiver can semi-coherently (under primary uncertainty) decode RIScatter nodes from the accumulated receive energy, re-encode to recover the exact reflection patterns, and combine those with cascaded \gls{csi} to determine the multipath response and model within the primary channel.
	Such a backscatter-primary decoding enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison, re-encoding, and precoding during each backscatter (instead of primary) block.
	It enjoys a three-fold benefit compared to conventional primary-backscatter decoding with \gls{sic}, namely
	1) reduces the re-encoding frequencies to $1/N$;
	2) requires no re-precoding, cancellation, or \gls{mrc};
	3) preserves backscatter modulation and passive beamforming at smaller spreading factors for potentially higher backscatter throughput.
	% \end{subsection}

>>>>

	% ? Add an illustration here if space allows
	We also propose a novel cooperative receiver that exploits the double modulation, double fading and symbol period difference to reduce the decoding complexity and improve the primary-backscatter tradeoff.
	As illustrated in Fig.~\ref{fg:energy_distribution}, conditioned on different reflection state hypotheses, the accumulated receive energy per backscatter block follows Gamma distribution with different scale parameters \cite{Qian2017b}.
	\begin{figure}[!t]
		\centering
		\resizebox{0.4\columnwidth}{!}{
			\input{assets/illustration/energy_distribution.tex}
		}
		\caption{
			\gls{pdf} of accumulated receive energy per backscatter block conditioned on different reflection state hypotheses.
			% $z$, $t$, $\mathcal{H}$ and $\mathcal{R}$ denote the accumulated receive energy, decision threshold, reflection state hypothesis, and decision regions, respectively.
		}
		\label{fg:energy_distribution}
	\end{figure}
	Hence, the receiver can semi-coherently (under primary uncertainty) decode RIScatter nodes from the accumulated receive energy, re-encode to recover the exact reflection patterns, and combine those with cascaded \gls{csi} to determine the multipath response and model within the primary channel.
	Such a backscatter-primary decoding enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison and re-encoding during each backscatter (instead of primary) block.
	It enjoys a three-fold benefit compared to conventional primary-backscatter decoding with \gls{sic}, namely
	1) reduces the re-encoding frequencies to $1/N$;
	2) requires no re-precoding, cancellation, or \gls{mrc};
	3) preserves backscatter modulation and passive beamforming at smaller spreading factors for potentially higher backscatter throughput.
	% \end{subsection}

### 2023-01-17 main.tex
:triangular_flag_on_post: JSAC 230117

		% ? Add an illustration here if space allows
		We also propose a novel cooperative receiver that exploits the double modulation, double fading and symbol period difference to reduce the decoding complexity and improve the primary-backscatter tradeoff.
		As illustrated in Fig.~\ref{fg:energy_distribution}, conditioned on different reflection state hypotheses, the accumulated receive energy per backscatter block follows Gamma distribution with different scale parameters \cite{Qian2017b}.
		\begin{figure}[!t]
			\centering
			\resizebox{0.8\columnwidth}{!}{
				\input{assets/illustration/energy_distribution.tex}
			}
			\caption{
				\gls{pdf} of accumulated receive energy per backscatter block conditioned on different reflection state hypotheses.
				$z$, $t$, $\mathcal{H}$ and $\mathcal{R}$ denote the accumulated receive energy, decision threshold, reflection state hypothesis, and decision regions, respectively.
			}
			\label{fg:energy_distribution}
		\end{figure}
		Hence, the receiver can semi-coherently (under primary uncertainty) decode RIScatter nodes from the accumulated receive energy, re-encode to recover the exact reflection patterns, and combine those with cascaded \gls{csi} to determine the multipath response and model within the primary channel.
		Such a backscatter-primary decoding enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison, re-encoding, and precoding during each backscatter (instead of primary) block.
		It enjoys a three-fold benefit compared to conventional primary-backscatter decoding with \gls{sic}, namely
		1) reduces the re-encoding frequencies to $1/N$;
		2) requires no re-precoding, cancellation, or \gls{mrc};
		3) preserves backscatter modulation and passive beamforming at smaller spreading factors for potentially higher backscatter throughput.
	\end{subsection}

>>>>

		% ? Add an illustration here if space allows
		We also propose a novel cooperative receiver that exploits the double modulation, double fading and symbol period difference to reduce the decoding complexity and improve the primary-backscatter tradeoff.
		As illustrated in Fig.~\ref{fg:energy_distribution}, conditioned on different reflection state hypotheses, the accumulated receive energy per backscatter block follows Gamma distribution with different scale parameters \cite{Qian2017b}.
		\begin{figure}[!t]
			\centering
			\resizebox{0.8\columnwidth}{!}{
				\input{assets/illustration/energy_distribution.tex}
			}
			\caption{
				\gls{pdf} of accumulated receive energy per backscatter block conditioned on different reflection state hypotheses.
				$z$, $t$, $\mathcal{H}$ and $\mathcal{R}$ denote the accumulated receive energy, decision threshold, reflection state hypothesis, and decision regions, respectively.
			}
			\label{fg:energy_distribution}
		\end{figure}
		Hence, the receiver can semi-coherently (under primary uncertainty) decode RIScatter nodes from the accumulated receive energy, re-encode to recover the exact reflection patterns, and combine those with cascaded \gls{csi} to determine the multipath response and model within the primary channel.
		Such a backscatter-primary decoding enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison and re-encoding during each backscatter (instead of primary) block.
		It enjoys a three-fold benefit compared to conventional primary-backscatter decoding with \gls{sic}, namely
		1) reduces the re-encoding frequencies to $1/N$;
		2) requires no re-precoding, cancellation, or \gls{mrc};
		3) preserves backscatter modulation and passive beamforming at smaller spreading factors for potentially higher backscatter throughput.
	\end{subsection}
